%%================================================
%% Filename: abstract.tex
%% Encoding: UTF-8
%% Author: Yuan Xiaoshuai - yxshuai@gmail.com
%% Created: 2012-04-24 00:21
%% Last modified: 2016-08-28 21:05
%%================================================
\addcontentsline{toc}{chapter}{摘要}
\begin{cabstract}

论文的摘要是对论文研究内容和成果的高度概括。摘要应对论文所研究的问题及其研究目
的进行描述，对研究方法和过程进行简单介绍，对研究成果和所得结论进行概括。摘要应
具有独立性和自创性，其内容应包含与论文全文同等量的主要信息。

论文摘要的书写应力求精确、简明。硕士学位论文建议1000字以内，博士学位论文建议
2000字以内。部分学生用外文撰写学位论文时，博士学位论文的摘要应不少于5000字符，
硕士应不少于2500字符。切忌写成对论文书写内容进行提要的形式，尤其要避免“第1章……
；第2章……；……”这种或类似的陈述方式。摘要中不可出现图片、图表、表格或其他插图材
料。

关键词是为了便于做文献索引和检索工作而从论文中选取出来用以表示全文主题内容信息
的单词或术语。关键词应体现论文特色，具有语义性，在论文中有明确的出处，并应尽量
采用《汉语主题词表》或各专业主题词表提供的规范词。在摘要内容下方另起一行标明，
一般3～8个，之间用空格分开。为便于国际交流，应标注与中文对应的英文关键词。

\zzuthesis{}（郑州大学学位论文模板）源代码来自清华大学学位论文模板（\textsc{ThuThesis}），由Xiaoshuai Yuan根据《郑州大学物理工程学院本科毕业设计（论文）基本规范》和《郑州大学学位论文写作规范格式》的规范修改得到；在此基础上，Fangyuan Li根据电气工程学院基本规范进行进一步修改，基本符合学校学院的相关要求。本文介绍该模板的使用方法，并给出相关示例。

本文的创新点主要有：
  \begin{itemize}
    \item 用例子来解释模板的使用方法；
    \item 用废话来填充无关紧要的部分；
    \item 一边摸索学习一边编写新代码；
    \item 惭愧地继承了前人绝大部分成果。
  \end{itemize}

\textsf{模板作者声明}：关键词分隔符用半角逗号，模板会自动处理替换为《规范》中
规定的分隔符，英文关键词同理。该分隔符在 \verb|zzuthesis.cfg| 中定义。

\ckeywords{\TeX{}/\LaTeX{}, \XeLaTeX{}与中文处理, 科技排版, 郑州大学, 学位论文
模板, 关于摘要}

\end{cabstract}

\addcontentsline{toc}{chapter}{Abstract}
\begin{eabstract} 

An abstract of a dissertation is a summary and extraction of research work and
contributions. Included in an abstract should be description of research topic
and research objective, brief introduction to methodology and research
process, and summarization of conclusion and contributions of the research. An
abstract should be characterized by independence and clarity and carry
identical information with the dissertation. It should be such that the
general idea and major contributions of the dissertation are conveyed without
reading the dissertation. 

An abstract should be concise and to the point. It is recommended that the
abstract of master thesis be less than 1000 characters, and the doctor
dissertation less than 2000 characters accordingly. For students who write
their thesis in foreign languages, the abstract should be no more than 2500 \&
5000 words respectively. It is a misunderstanding to make an abstract an
outline of the dissertation and words ``the first chapter'', ``the second
chapter'' and the like should be avoided in the abstract. No pictures, charts,
tables or illustrations are allowed in the abstract.

Key words are terms used in a dissertation for indexing, reflecting core
information of the dissertation. An abstract may contain 3$\sim$8 key words,
with comma used in between to separate one another. In order to facilitate
international exchanges, Enlish keywords should be marked on the corresponding
keywords in Chinese.

\ekeywords{\TeX/\LaTeX, \XeLaTeX\&Chinese, Scientific typesetting system,
Academic thesis template, Zhengzhou University, About keywords}

\end{eabstract}
